Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-03-09 hotstorage13/eval.tex
add graph

\begin{verbatim}
q= is chosen between 500 or 100
Memory limit:   20 30M   50M  75M  100M  200M
Time:          3.2  3.11   3  2.99 2.96  2.95
Time for two scans: 2.78 2.78 2.78 2.78 2.78
\end{verbatim}

Table~\ref{tab:memory} shows the performance of partition-based deduplication when 
the memory limit imposed on each node, varying from 
The overall processing time does not have a significant reduction as we increase memory usage  20MB to 200MB.
As Row 2 shows, the time is mainly dominated by  the IO costs of two scans of VMs.
Thus we conclude that using about 30MB is sufficient to have VM backup completed in parallel within about 3.11 hours.

>>>>

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{mem_time.eps}
\caption{Performance of partition-based deduplication under different memory limits}
\label{fig:memory}
\end{figure}

% \begin{verbatim}
% q= is chosen bteween 500 or 100
% Memory limit:   20 30M   50M  75M  100M  200M
% Time:          3.2  3.11   3  2.99 2.96  2.95
% Time for two scans: 2.78 2.78 2.78 2.78 2.78
% \end{verbatim}

Figure~\ref{fig:memory} shows the performance of partition-based deduplication when 
the memory limit imposed on each node, varying from 
The overall processing time does not have a significant reduction as we increase memory usage  20MB to 200MB.
As Row 2 shows, the time is mainly dominated by  the IO costs of two scans of VMs.
Thus we conclude that using about 30MB is sufficient to have VM backup completed in parallel within about 3.11 hours.
